Joint Neighborhood Subgraphs Link Prediction

### 2017-06-30 paper.tex
F

\subsection{Node labeling}
NSPDK takes labeled graphs as its input to proceed. Therefore, graph node labeling is a step needs to be done before employing NSPDK for graph similarity measure. Here, we propose a node labeling function $\ell$ which assigns labels for nodes based on node degrees. First, we use the degree values for their labels for nodes having degree less than or equal 5. We then discretize the degrees larger than 5 into k bins and assign the same label for nodes belong to the same bin. We label for nodes owning similar degrees with the same label due to the assumption that nodes with similar degrees tend to share common properties. Formally, the function is defined as:
\begin{center}
$\ell(u) = \left\{
	\begin{array}{ll}
		d(u),\  & \mbox{if } d(u) \leq 5 \\
		5+i,\ & \mbox{if } d(u) > 5
	\end{array}
\right.$,
\end{center}
where $i = \lceil \frac{d(u)-5}{bin}\rceil$, $bin = \frac{d(G)-5}{\lambda - 5}$ and $\lambda$ ($\lambda > 5$) is the number of labels used to label for nodes in the graphs. The value of $\lambda$ depend on the histogram of graph node degree. We can use tuning technique in order to obtain suitable value for $\lambda$.
\subsection{Link representation}
Most methods for link prediction attempt to computes similarities between nodes and consider to rank links. We desire to take links as examples to learn and predict. Therefore, we propose a method which model the context of two nodes to represent for link connecting them.

>>>>

\subsection{Node labeling}
NSPDK takes labeled graphs as its input to proceed. Therefore, graph node labeling is a step needs to be done before employing NSPDK for graph similarity measure. Here, we propose a node labeling function $\ell$ which assigns labels for nodes based on node degrees. First, we use the degree values for their labels for nodes having degree less than or equal 5. We then discretize the degrees larger than a user defined threshold $T$ ($T=5$ in our experimental evaluation) into $k$ bins and assign the same label for nodes belong to the same bin. We label for nodes owning similar degrees with the same label due to the assumption that nodes with similar degrees tend to share common properties. Formally, the function is defined as:
\begin{center}
$\ell(u) = \left\{
	\begin{array}{ll}
		d(u),\  & \mbox{if } d(u) \leq T \\
		T+i,\ & \mbox{if } d(u) > T
	\end{array}
\right.$,
\end{center}
where $i = \lceil \frac{d(u)-T}{bin}\rceil$, $bin = \frac{d(G)-T}{\lambda - T}$ and $\lambda$ ($\lambda > T$) is the number of labels used to label for nodes in the graphs. The value of $\lambda$ depend on the histogram of graph node degree. We can use tuning technique in order to obtain suitable value for $\lambda$.
\subsection{Link representation}
Most methods for link prediction attempt to computes similarities between nodes and consider to rank links. We desire to take links as examples to learn and predict. Therefore, we propose a method which model the context of two nodes to represent for link connecting them.
